Implications of afforestation policies for global markets

### 2024-02-28 paper.Rmd
Update paper.Rmd

# Deforestation under the baseline projections

To understand the impact of potential regional and global afforestation actions, an important first step was creating a realistic baseline scenario that depicts the likely changes over the decade under study, 2023--2033. Data for this were drawn from CEPII [@CEPII2024]. To build our scenario, we used two key projected variables by CEPII: population and GDP. The CEPII projections do not contain any information on land use. To build a more complete baseline, we also include the projections on forested land change included in the Global Timber Model (GTM). Using the GTAP model in connection with the GTM model (to assure that the changes in land are consistent between the two models), we calculate the overall change in factor quantity/productivity growth required to achieve the targeted values in 2033. In Table \@ref(tab:baseline-growth) we show the projected population and GDP growths per region.

>>>>

# Changes under the baseline projections

To understand the impact of potential regional and global afforestation actions, an important first step was creating a realistic baseline scenario that depicts the likely changes over the decade under study, 2023--2033. Data for this were drawn from CEPII [@CEPII2024]. To build our scenario, we used two key projected variables by CEPII: population and GDP. The CEPII projections do not contain any information on land use. To build a more complete baseline, we also include the projections on forested land change included in the Global Timber Model (GTM). Using the GTAP model in connection with the GTM model (to assure that the changes in land are consistent between the two models), we calculate the overall change in factor quantity/productivity growth required to achieve the targeted values in 2033. In Table \@ref(tab:baseline-growth) we show the projected population and GDP growths per region. GDP increases for all regions of the world with the largest percentage changes occurring in South Asia (+308.6%), China (+189.8%), and Sub-Saharan Africa (+172.9%). Population also is projected to grow in most regions with the largest changes happening in Sub-Saharan Africa (+55.7%). Japan, Russia, and East Asia are projected to see their populations decline by 10.4%, 4.7%, and 2.6%, respectively. As for the projected change in agricultural land, baseline estimates show significant growth in Oceania (+27.6%), Rest of Latin America (+25.8%), Sub-Saharan Africa (+17.4%), Central America (+13.9%), and Brazil (+13.9%). Japan is the only nation that sees a significant decline (-34.9%) in agricultural land, which is likely tied in part to the population decline described above.
